The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-08-20 script/en/chapters/what-is-sage.tex
Script[de+en]: hanging indent in footnotes; corrected links to old appendix parts

\noindent With respect to studying cryptography, Sage modules can be used
to complement a first course in cryptography\footnote{%
- Module sources in the directory \url{SAGE_ROOT/devel/sage-main/sage/crypto}.\\
- Overview, what crypto currently is in Sage:\\
~ ~ \url{http://www.sagemath.org/doc/reference/sage/crypto/}\\
- Discussions about teaching related aspects of development crypto in Sage:\\
~ ~ \url{http://groups.google.com/group/sage-devel/browse_thread/thread/c5572c4d8d42d081}
}.

@@

\noindent To program and test Sage code using an editor there are two useful commands:
\verb!load()! and \verb!attach()!\footnote{%
See Sage tutorial about Programming, chapter ``Loading and Attaching SAGE files'',\\
\url{http://www.sagemath.org/doc/tutorial/programming.html\#loading-and-attaching-sage-files}.}.\\
Suppose you have a function definition like this:
\begin{Verbatim}%
   [fontsize=\footnotesize,fontshape=tt]
   def function(var1):
       r"""
       DocText.
       """
       ...
       return (L)
\end{Verbatim}
\noindent which has been saved to the file \texttt{primroots.sage}.

@@

\noindent and you can then proceed to use on the command line anything that is
defined in that Sage script\footnote{%
Notes:\\
- Don't use white spaces in your file name.\\
- Its recommended that your Sage script has the file extension
``.sage'', instead of ``.py''. With a Sage script whose file name ends in
``.sage'', when you load it into Sage then the default Sage environment
is also loaded to make sure that it works as if you have defined your
function from the Sage command line. This also applies if you run the
script from a bash shell using~~\texttt{\$ sage primroots.sage}.

If you run your script as above, then Sage first parses your script,
writes it to another file called ``primroots.py'' (note the ``.py''
extension), adds all necessary variables to "primroots.py" as well as
writing any import statements to that file. That way, your Sage script
is executed as if you had typed the definitions in your script to the
Sage command line. A difference may be that output needs a print statement.}.

@@

Here is a picture of Sage code in the editor GVIM with activated code highlighting
~(see figure~\ref{fig:sage-highlighted-code-in-editor}).
%
\begin{figure}[!htpb]
\centering
\includegraphics[scale=0.7]{figures/sage-highlighted-code-in-editor}
\caption{Sage sample shown in an editor with code highlighting}
\label{fig:sage-highlighted-code-in-editor}
\end{figure}

\vspace{30pt}
\noindent To get the version of your Sage environment:
\texttt{version()}

\noindent To move quickly to the Sage code examples in this script,\\
- either look in the index at \verb#Sage -> Code examples#,\\
- or have a look at the appendix ``\nameref{sc:List-of-Sage-Code-Examples}''.

>>>>

\noindent With respect to studying cryptography, Sage modules can be used
to complement a first course in cryptography\footnote{%
- Module sources in the directory \url{SAGE_ROOT/devel/sage-main/sage/crypto}.

\noindent\hangindent=6pt\makebox[6pt][l]{-}Overview, what crypto currently is in Sage:\\
   \url{http://www.sagemath.org/doc/reference/sage/crypto/}

\noindent\hangindent=6pt\makebox[6pt][l]{-}Discussions
   about teaching related aspects of development crypto in Sage:\\
   \url{http://groups.google.com/group/sage-devel/browse_thread/thread/c5572c4d8d42d081}

   % Leerzeile am Ende nötig, sonst hat die zweite Zeile KEINEN hängenden Einzug?! (TODO)
   % Dadurch aber mehr Abstand von Seitennummer als sonst!
}.

@@

\noindent To program and test Sage code using an editor there are two useful commands:
\verb!load()! and \verb!attach()!\footnote{%
See Sage tutorial about Programming, chapter ``Loading and Attaching Sage files'',\\
\url{http://www.sagemath.org/doc/tutorial/programming.html\#loading-and-attaching-sage-files}.}.\\
Suppose you have a function definition like this:
\begin{Verbatim}%
   [fontsize=\footnotesize,fontshape=tt]
   def function(var1):
       r"""
       DocText.
       """
       ...
       return (L)
\end{Verbatim}
\noindent which has been saved to the file \texttt{primroots.sage}.

@@

\noindent and you can then proceed to use on the command line anything that is
defined in that Sage script\footnote{%
Notes:

\noindent\hangindent=6pt\makebox[6pt][l]{-}Don't use white spaces in your file name.

\noindent\hangindent=6pt\makebox[6pt][l]{-}Its recommended that your Sage script
has the file extension
``.sage'', instead of ``.py''. With a Sage script whose file name ends in
``.sage'', when you load it into Sage then the default Sage environment
is also loaded to make sure that it works as if you have defined your
function from the Sage command line. This also applies if you run the
script from a bash shell using~~\texttt{\$ sage primroots.sage}.

\noindent\hangindent=6pt\makebox[6pt][l]{-}If you run your script as above,
then Sage first parses your script,
writes it to another file called ``primroots.py'' (note the ``.py''
extension), adds all necessary variables to "primroots.py" as well as
writing any import statements to that file. That way, your Sage script
is executed as if you had typed the definitions in your script to the
Sage command line. A difference may be that output needs a print statement.

}.

@@

Here is a picture of Sage code in the editor GVIM with activated code highlighting
(see figure~\ref{fig:sage-highlighted-code-in-editor}).
%
\begin{figure}[!htpb]
\centering
\includegraphics[scale=0.7]{figures/sage-highlighted-code-in-editor}
\caption{Sage sample shown in an editor with code highlighting}
\label{fig:sage-highlighted-code-in-editor}
\end{figure}

\vspace{30pt}
\noindent Some more hints:
\begin{itemize}
  \item To get the version of your Sage environment: \texttt{version()}
  \item To move quickly to the Sage code examples in this script,
    \begin{itemize}
      \item either look in the index at \verb#Sage -> Code examples#,
      \item or have a look at the appendix ``\nameref{sc:List-of-Sage-Code-Examples}''.
  \end{itemize}
\end{itemize}
